### 2023-09-22 doc/15yrsChange.Rmd
change how we describe focal areas
@llmorreale , I think it makes sense to present the areas as (a) low deer, low non-endemic insects & pathogens, (b) high deer, low non-endemic insects & pathogens, (c) high deer, high non-endemic insects & pathogens (in that order). This stems from your comment yesterday, and also thinking we should present this as progressive degradation.

#Figures
map_and_photos = 1
photo_represenative_upland = "1a"
photo_deer_exclosure = "1b"
photo_graveyard = "1c"

@@

loss_gain_net = 3 # 4-panel figure showing ∆AGB, loss, and gain for (a) whole plot, (b) upland, (c) deer exclosure, (d) graveyard

mortality_by_genera = 4 # 4-panel figure showing biomass mortality by genera for for (a) whole plot, (b) upland, (c) deer exclosure, (d) graveyard

@@

In addition to our consideration of the plot as a whole, we give special consideration to three portions of the plot:
(1) representative upland forest (Fig. `r photo_represenative_upland`) - # ha of the plot, excluding areas around streams (*delineated using topographic wetness index, described in @mcgregor_tree_2021*) and the two special focal areas
(2) deer exclosure (Fig. `r photo_deer_exclosure`)- 4 ha portion of upland forest in the SE quarter of the plot, fenced in YEAR and maintained mainly deer-free for the past ## years;
(3) "tree graveyard" (Fig. `r photo_graveyard`) - a # ha section of upland forest in the NE corner of the plot where extensive mortality of *Fraxinus* and other canopy trees within the past decade has resulted in an open canopy and heavy ground cover of invasive plants. 
The latter was delineated based on *(define & describe criteria)*

![**Figure `r map_and_photos`. Photos within the SCBI ForestGEO plot: (a) represenative upland forest, (b) deer exclosure, (c) "tree graveyard" in NE corner ** *(Perhaps combine these with a map of the plot?)*](display/photos.png)

>>>>

#Figures
map_and_photos = 1
photo_deer_exclosure = "1a"
photo_represenative_upland = "1b"
photo_graveyard = "1c"

@@

loss_gain_net = 3 # 4-panel figure showing ∆AGB, loss, and gain for (a) whole plot, (b) deer exclosure, (c) upland, (d) graveyard

mortality_by_genera = 4 # 4-panel figure showing biomass mortality by genera for for (a) whole plot, (b) deer exclosure, (c) upland, (d) graveyard

@@

In addition to our consideration of the plot as a whole, we give special consideration to three portions of the plot, all upland forest (i.e., excluding low-lying areas around streams):
(1) low deer, low non-endemic insects & pathogens (Fig. `r photo_deer_exclosure`)- 4 ha portion of upland forest in the SE quarter of the plot, fenced in YEAR and maintained with only occasional deer presence for the past ## years and with relatively low abundance of canopy species affected by non-endemic pests and pathogens;
(2) high deer, low non-endemic insects & pathogens (Fig. `r photo_represenative_upland`) - # ha of upland forest outside the deer exclosure with relatively low abundance of canopy species affected by non-endemic pests and pathogens; 
(3) high deer, high non-endemic insects & pathogens (Fig. `r photo_graveyard`) - a # ha section of upland forest outside the deer exclosure with relatively high abundance of canopy species affected by non-endemic pests and pathogens. 
These areas were delineated as follows.
Upland forest was defined according to topographic wetness index, originally calculated for the SCBI plot in @mcgregor_tree_2021.
Vulnerability to non-endemic insects & pathogens was defined based on the abundance of canopy species affected by non-endemic pests and pathogens at the time of plot establishment (2008).

![**Figure `r map_and_photos`. Photos within the SCBI ForestGEO plot: (a) low deer, low non-endemic insects & pathogens, (b) high deer, low non-endemic insects & pathogens, (c) high deer, high non-endemic insects & pathogens ** *(add a map of the plot)* All photos taken September 2023 by K. Anderson-Teixeira.](display/photos.png)
